Results

### 2025-09-03 index.qmd
feat: add alpha
feat: add cross_helicity and residual energy

@lotekarKineticscaleCurrentSheets2022

@@

>>>>

@lotekarKineticscaleCurrentSheets2022
@perroneCoherentEventsIon2020

@@

“Knetter [2005] extended this work to intervals in 2002 and 2003 which also included fast wind intervals. He obtained similar results to above and amassed a final total collection of 366 discontinuities. All of the discontinuities had normal field components consistent with zero. He concluded that the discontinuities are best explained as TDs regardless of the amount of dB/B.” ([Vasquez et al., 2007, p. 2](zotero://select/library/items/VPNY4UFZ)) ([pdf](zotero://open-pdf/library/items/DNN2ADMT?page=2&annotation=9Q8CVTE9))

### 2025-09-03 notebooks/00_index.qmd
feat: add cross_helicity and residual energy

update_theme!(;
    figure_padding=1,
    fonts=(; regular=AoG.firasans("Regular"), bold=AoG.firasans("Medium")),
    Legend=(; framevisible=false, padding=(0, 0, 0, -15)),
    Axis=(; xlabelfont=:bold, ylabelfont=:bold),
)
```

@@

foreach([:log10, :log2, :log]) do f
    @eval import Base: $f
    @eval $f(x::Unitful.Quantity) = $f(ustrip(x))
end

>>>>

set_Z_theme!()
```

@@

### 2025-09-03 notebooks/02_stats.qmd
feat: add cross_helicity and residual energy

```{julia}
using StatsBase, Statistics
using PSPAnisotropy
using Discontinuity: compute_params!, filter_low_mva_quality
using Discontinuity: compute_Alfvenicity_params!, Alfven_velocity
using DimensionalData
using DataFrames, DataFramesMeta
using GLMakie
using Beforerr: _theme_legend, easy_save
using AlgebraOfGraphics
import AlgebraOfGraphics as AoG

𝐧 = :mva
𝒎 = var_mapping(; 𝐧)

using Unitful
Unitful.preferunits(u"nA", u"km")
unitify(u) = (*)$u
unitify(u::String) = (*)$uparse(u)

taus = Second.(2 .^ (1:6))
df = workload(taus)
Discontinuity.assign_accuracy!(df)
@chain df begin
    compute_Alfvenicity_params!()
    compute_params!()
end
```

@@

```{julia}
subset_𝐧(df, 𝐧) = 𝐧 == :mva ? filter_low_mva_quality(df) : df
fname = "properties_hist-enc"

@@

    tdf = @chain df begin
        @subset(.!isnan.(:L_n_mva_norm); view=true)
        subset_𝐧(𝐧)
        dropmissing(:L_n_mva_norm)
        # compute_Alfvenicity_params!
    end

@@

    plt = data(tdf) *
          mapping(vars, layout=AoG.dims(1) => renamer(labels)) *
          mapping(color=:id, linestyle=:enc) *
          AoG.density(; datalimits) * visual(Lines)
    draw(plt, axis=(; yscale=log10))

    # draw(spec, scales(Layout=(; palette=wrapped(cols=2))); facet=(; linkyaxes=:none))
    # easy_save("$fname-$enc-$𝐧"; formats, force=true)
end
fs[1]
```

```{julia}

    tdf = @chain df begin
        @subset(.!isnan.(:V_l_ratio); view=true)
        subset_𝐧(𝐧)
        dropmissing(:V_l_ratio)
        # compute_Alfvenicity_params!
    end

    vars = [:Q_sonnerup, 𝒎.v_l_ratio, :V_l_ratio_max]
    # 𝒎.v_l_ratio, 𝒎.bn
    labels = ["Alfvénicity", "Velocity ratio", "Max velocity ratio"]

    plt = data(tdf) *
          mapping(vars, layout=AoG.dims(1) => renamer(labels)) *
          mapping(color=:id, linestyle=:enc) *
          AoG.density(; datalimits) * visual(Lines)
    draw(plt, axis=(; yscale=log10))

    # draw(spec, scales(Layout=(; palette=wrapped(cols=2))); facet=(; linkyaxes=:none))
    # easy_save("$fname-$enc-$𝐧"; formats, force=true)
end
fs[1]

```

@@

```{julia}
let df = dropmissing(df, :duration)
    df.duration = ustrip.(df.duration .|> u"s")
    layer = AoG.density(; datalimits=x -> quantile(x, [0.02, 0.99])) * visual(Lines) * mapping(linestyle=:id)
    # layer = AoG.histogram(; datalimits=x -> quantile(x, [0.02, 0.99]), bins = 0:0.3:30) * mapping(col=:id)
    plt = data(df) * mapping(:duration, color=:enc) * layer
    plt = plt + mapping(2 .^ (1:4)) * visual(VLines, color=:gray, linestyle=:dash)
    # plt *= (mapping(col=direct("col1")) + mapping(color=:tau, col=direct("col2")))
    # scales(Col=(; legend=false))
    draw(plt, axis=(; yscale=log10))
end
```

@@

```{julia}
let df = dropmissing(df, :duration)
    df.duration = ustrip.(df.duration .|> u"s")
    plt = data(df) * mapping(:duration, linestyle=:id, color=:enc) * AoG.density(; datalimits=x -> quantile(x, [0.02, 0.98])) * visual(Lines)
    plt *= mapping(col=:tau)
    draw(plt, axis=(; yscale=log10), facet=(; linkxaxes=:none, linkyaxes=:none))
end
```

>>>>

```{julia}
using Dates
using StatsBase, Statistics
using PSPAnisotropy
import Discontinuity as DC
using Discontinuity: var_mapping, compute_params!, filter_low_mva_quality
using Discontinuity: compute_Alfvenicity_params!, Alfven_velocity
using DimensionalData
using DataFrames, DataFramesMeta
using CairoMakie
using Beforerr: _theme_legend, easy_save
using AlgebraOfGraphics
import AlgebraOfGraphics as AoG
using Unitful
Unitful.preferunits(u"nA", u"km")

# https://github.com/MakieOrg/AlgebraOfGraphics.jl/issues/464
foreach([:log10, :log2, :log]) do f
    @eval import Base: $f
    @eval $f(x::Unitful.Quantity) = $f(ustrip(x))
end
set_Z_theme!()
formats = (:pdf,)
```

```{julia}
𝐧 = :mva
𝒎 = var_mapping(; 𝐧)

taus = Second.(2 .^ (1:6))
# taus = Second.(2 .^ (0:6))
df = workload(taus)
@chain df begin
    DC.compute_Alfvenicity_params!()
    DC.compute_params!()
    @transform!(:B_n_mva_norm = abs.(:B_n_mva ./ :B_mag))
    DC.classify!(:B_n_mva_norm)
end

# Count the number of events for each type
df_event_counts = @chain df begin
    groupby(:type)
    combine(nrow)
end
```

@@

Density distributions of (normalized) thickness and current density

```{julia}
subset_𝐧(df, 𝐧) = 𝐧 == :mva ? filter_low_mva_quality(df) : df
fname = "properties_hist"

@@

    tdf = @chain df begin
        @subset(.!isnan.(:L_n_mva_norm); view=true)
        # @rsubset(((:id == "PSP") && :tau <= Second(2)) || (:id != "PSP" && :tau > Second(2))) # select current sheet events with tau <= 2s for PSP and tau > 2s for Earth
        subset_𝐧(𝐧)
        dropmissing(:L_n_mva_norm)
    end

@@

    plt =
        data(tdf) *
        mapping(vars, layout=AoG.dims(1) => renamer(labels)) *
        # mapping(vars, row=AoG.dims(1) => renamer(labels), col=:type) *
        mapping(color=:id, linestyle=:enc) *
        AoG.density(; datalimits) * visual(Lines)
    draw(plt, axis=(; yscale=log10))
    easy_save("$fname-$𝐧"; formats, force=true)
end
fs[1]
```

@@

```{julia}
let df = dropmissing(df, :duration)
    df.duration = ustrip.(df.duration .|> u"s")
    layer = AoG.density(; datalimits=x -> quantile(x, [0.02, 0.99])) * visual(Lines)
    # layer = AoG.histogram(; datalimits=x -> quantile(x, [0.02, 0.99]), bins = 0:0.3:30) * mapping(col=:id)
    plt = data(df) * mapping(:duration, linestyle=:enc, color=:id) * layer
    plt = plt + mapping(2 .^ (1:4)) * visual(VLines, color=:gray, linestyle=:dash)
    # plt *= (mapping(col=direct("col1")) + mapping(color=:tau, col=direct("col2")))
    # scales(Col=(; legend=false))
    draw(plt, axis=(; yscale=log10))
    easy_save("duration_dist"; formats, force=true)
end
```

@@

```{julia}
let df = dropmissing(df, :duration)
    df.duration = ustrip.(df.duration .|> u"s")
    layer = AoG.density(; datalimits=x -> quantile(x, [0.02, 0.99])) * visual(Lines)
    plt = data(df) * mapping(:duration, linestyle=:enc, color=:id) * layer
    plt *= mapping(layout=:tau)
    draw(plt, axis=(; yscale=log10), facet=(; linkxaxes=:none, linkyaxes=:none))
    easy_save("duration_dist_tau"; formats, force=true)
end
```

```{julia}
𝒎 = var_mapping(; 𝐧)

tdf = @chain df begin
    @subset(.!isnan.(:V_l_ratio); view=true)
    subset_𝐧(𝐧)
    dropmissing(:V_l_ratio)
end

vars = [:Q_sonnerup => abs => "", :ΔV_ratio => identity => "", :V_l_ratio => identity => "", :V_l_ratio_max => identity => ""]
# 𝒎.v_l_ratio, 𝒎.bn
labels = ["Q_sonnerup", "Δ V ratio", "ΔV_l ratio", "Max ΔV_l ratio"]

plt =
    data(tdf) *
    mapping(vars, row=AoG.dims(1) => renamer(labels)) *
    #   mapping(vars, col=:tau, row=AoG.dims(1) => renamer(labels)) *
    mapping(color=:id, linestyle=:enc) *
    AoG.density(; datalimits) * visual(Lines)
draw(plt, axis=(; yscale=identity), facet=(; linkyaxes=:minimal))
# easy_save("Alfvenicities"; formats, force=true)
# draw(spec, scales(Layout=(; palette=wrapped(cols=2))); facet=(; linkyaxes=:none))
```

##

Joint distributions of thickness and current density

```{julia}
for 𝐧 in [:mva]
    view = true
    𝒎 = var_mapping(; 𝐧)

    tdf = @chain df begin
        # @subset(:enc .== enc)
        dropmissing()
        @transform(:L_n_mva = Float64.(ustrip.(:L_n_mva)), :J_m_max_mva = Float64.(ustrip.(:J_m_max_mva)))
        subset_𝐧(𝐧)
    end

    plt = alpha_layer(tdf, 0.618) * visual(Scatter; markersize=6, legend=(; alpha=0.6)) * mapping(color=:id, marker=:id)

    fig = Figure(size=(800, 300))
    axis = (; yscale=log10, xscale=log10)
    v_axis = (; yscale=log10, xscale=log10, limits=((2, 400), (2, 400)))

    ga = fig[1, 1]
    gb = fig[1, 2]
    gc = fig[2, 1]
    gd = fig[2, 2]

    spec1 = plt * mapping(𝒎.l, 𝒎.j)
    spec2 = plt * mapping(𝒎.l_norm, 𝒎.j_norm)
    spec3 = plt * mapping(:B_n_mva_norm, :ω)
    spec4 = plt * mapping(:ΔV_ratio, :ΔV_cosθ)

    grid1 = draw!(ga, spec1; axis)
    draw!(gb, spec2; axis)
    draw!(gc, spec3)
    draw!(gd, spec4; axis=(; limits=((0, 2), (-1, 1),)))

    # pretty_legend!(fig, grid1)
    # add_labels!([ga, gb, gc])
    # easy_save("$fname-$enc-$𝐧"; formats, force=true)
    display(fig)
end
```

```{julia}
for 𝐧 in [:mva]
    view = true
    𝒎 = var_mapping(; 𝐧)

    tdf = @chain df begin
        @subset(.!isnan.(:B_n_mva_norm) .& .!isnan.(:σ_c); view=true)
        dropmissing([:B_n_mva_norm, :duration, :σ_c])
        @transform!(:duration = Float64.(ustrip.(:duration .|> u"s")))
        subset_𝐧(𝐧)
    end

    plt = data(tdf) * mapping(row=:id, col=:enc)
    vis = visual(Scatter; markersize=6)
    fig = Figure(; size=(1200, 800))
    axis = (;)

    ΔV_cosθ_group = :ΔV_cosθ => >(0)
    ΔV_cosθ_map = mapping(group=ΔV_cosθ_group, color=ΔV_cosθ_group)

    B_n_spec = plt * mapping(:B_n_mva_norm, :ω_in) * vis
    ΔV_spec = plt * mapping(:ΔV_ratio, :ΔV_cosθ) * (vis + AoG.smooth() * ΔV_cosθ_map)
    σc_σr_spec = plt * mapping(:σ_c, :σ_r) * (vis + AoG.smooth() * visual(color=:red))

    draw!(fig[1, 1], B_n_spec; axis)
    draw!(fig[1, 2], ΔV_spec; axis=(; limits=((0, 2), (-1, 1),)))
    draw!(fig[2, 1], σc_σr_spec)

    # pretty_legend!(fig, grid1)
    # add_labels!([ga, gb, gc])
    # easy_save("$fname-$enc-$𝐧"; formats, force=true)
    display(fig)
end
```

Joint distributions of Q_sonnerup and other variables

```{julia}
CairoMakie.activate!()

view = true
𝒎 = var_mapping(; 𝐧)

vars = [:B_n_mva_norm, :Q_sonnerup, :duration, :σ_c]

tdf = @chain df begin
    dropmissing(vars)
    @rsubset(all(!isnan, (:B_n_mva_norm, :Q_sonnerup, :σ_c)); view=true)
    @transform!(
        :duration = Float64.(ustrip.(:duration .|> u"s")),
        :B_n_mva_norm = Float64.(:B_n_mva_norm),
    )
end

A_He_df = @chain tdf begin
    dropmissing(:A_He)
    @transform!(:A_He = Float64.(only.(:A_He)))
    @rsubset(:A_He < 10)
end

Bn_df = subset_𝐧(tdf, 𝐧)

fig = Figure(; size=(1200, 800))
axis = (;)

layout = mapping(row=:id, col=:enc)
plt = data(tdf) * layout
vis = visual(Scatter; markersize=6)

Q_group = mapping(group=:Q_sonnerup => >(0), color=:Q_sonnerup => >(0))
A_He_group = mapping(group=:A_He => >(0), color=:A_He => >(0))
line_vis = visual(linewidth=3)

Bn_Q_spec = data(Bn_df) * mapping(:B_n_mva_norm, :Q_sonnerup) * layout * (vis + AoG.linear() * Q_group * line_vis)
duration_Q_spec = plt * mapping(:duration, :Q_sonnerup) * (vis + AoG.smooth() * Q_group * line_vis)
σc_Q_spec = plt * mapping(:σ_c, :Q_sonnerup) * (vis + AoG.linear() * Q_group * line_vis)
σr_Q_spec = plt * mapping(:σ_r, :Q_sonnerup) * (vis + AoG.linear() * Q_group * line_vis)
A_He_Q_spec = data(A_He_df) * mapping(:A_He, :Q_sonnerup => abs) * layout * (vis + AoG.smooth() * A_He_group * line_vis)

draw!(fig[1, 1], Bn_Q_spec)
draw!(fig[1, 2], duration_Q_spec; axis=(; xscale=log10))
draw!(fig[2, 1], σc_Q_spec)
draw!(fig[2, 2], σr_Q_spec)
draw!(fig[3, 1], A_He_Q_spec)

# add_labels!([ga, gb, gc])
# easy_save("Q_sonnerup_joint_dist"; formats, force=true)
display(fig)
```

## Duration vs Alfvénicity Correlation

Let's analyze the relationship between duration and Alfvénicity to see if they are correlated.

```{julia}
using HypothesisTests
using NaNStatistics
using PairPlots

# Filter for clean data with both duration and Alfvénicity measures
vars = [:duration, :Q_sonnerup, :V_l_ratio, :B_n_mva_norm]

df_corr = @chain df begin
    filter_low_mva_quality()
    dropmissing(vars)
    @transform!(:duration = Float64.(ustrip.(:duration .|> u"s")))
    @rsubset(all(!isnan, (:Q_sonnerup, :V_l_ratio, :duration, :σ_c)))
end

# Overall correlation matrix
println("Overall correlation matrix:")
cor_vars = [:Q_sonnerup, :duration, :B_n_mva_norm, :σ_c, :σ_r, :L_n_mva_norm, :J_m_max_mva_norm]
overall_corr = nancor(Matrix(df_corr[!, cor_vars]))
display(overall_corr)
# heatmap(cor_vars, cor_vars, overall_corr)
# pairplot(df_corr[!, cor_vars])

# Group by different missions and compute correlations
println("\nCorrelation analysis by mission:")
mission_stats = @chain df_corr begin
    groupby(:id)
    @combine(
        :count = nrow,
        :corr_Q_duration = nancor(:Q_sonnerup, :duration),
        :corr_Bn_duration = nancor(:B_n_mva_norm, :duration),
        :corr_Q_Bn = nancor(:Q_sonnerup, :B_n_mva_norm),
        :mean_Q = nanmean(abs.(:Q_sonnerup)),
        :mean_duration = nanmean(:duration),
        :mean_Bn = nanmean(:B_n_mva_norm)
    )
end

display(mission_stats)

# # Statistical significance tests
# test_q = CorrelationTest(df_corr.duration_s, df_corr.Q_sonnerup)
# test_vl = CorrelationTest(df_corr.duration_s, collect(skipmissing(df_corr.V_l_ratio)))

# println("Statistical significance:")
# println("Duration vs Q_sonnerup: p-value = $(round(pvalue(test_q), digits=6))")
# println("Duration vs V_l_ratio: p-value = $(round(pvalue(test_vl), digits=6))")
```

Correlation Strength:
- Duration vs Q_sonnerup: r = -0.0253 (very weak negative correlation)
- Duration vs V_l_ratio: r = -0.0134 (very weak negative correlation)

Statistical Significance:
- Duration vs Q_sonnerup: p = 0.009 (statistically significant, p < 0.05)
- Duration vs V_l_ratio: p = 0.166 (not statistically significant, p > 0.05)

Interpretation:
1. There is a very weak negative correlation between duration and Alfvénicity - meaning longer events tend to be slightly less Alfvénic
2. The effect size is tiny (correlations ~-0.02 to -0.03) - practically negligible
3. Only Q_sonnerup shows statistical significance due to the large sample size (10,684 events)
4. The large sample size makes even tiny correlations statistically detectable, but they're not practically meaningful

Conclusion: While there's a statistically significant but extremely weak tendency for longer-duration current sheets to be slightly less Alfvénic, the correlation is so small it's essentially negligible in practical terms. Duration and Alfvénicity are largely independent of each other in this dataset.

## Unused Code

```{julia}
# Visualization: Scatter plot with trend line
f_corr = Figure(size=(1400, 600))

attrs = (alpha=0.6, markersize=6)

# Duration vs Q_sonnerup
ax1 = Axis(f_corr[1, 1],
    xscale=log10,
    xlabel="Duration (seconds)",
    ylabel="Q_sonnerup (Alfvénicity)",
    title="Duration vs Alfvénicity")

scatter!(ax1, df_corr.duration_s, abs.(df_corr.Q_sonnerup); color=:blue, attrs...)

# Add trend line (remove any remaining NaNs)
valid_idx = .!isnan.(df_corr.duration_s) .& .!isnan.(df_corr.Q_sonnerup)
if sum(valid_idx) > 0
    x_valid = df_corr.duration_s[valid_idx]
    y_valid = abs.(df_corr.Q_sonnerup[valid_idx])
    x_range = range(minimum(x_valid), maximum(x_valid), length=100)
    X = hcat(ones(length(x_valid)), x_valid)
    β = X \ y_valid
    trend_y = β[1] .+ β[2] .* x_range
    lines!(ax1, x_range, trend_y, color=:red, linewidth=2, linestyle=:dash)
end

# text!(ax1, 0.05, 0.95, "r = $(round(corr_duration_q, digits=4))", space=:relative, fontsize=12, color=:black)

# Duration vs V_l_ratio  
df_vl = dropmissing(df_corr, :V_l_ratio)
ax2 = Axis(f_corr[1, 2],
    xscale=log10,
    xlabel="Duration (seconds)",
    ylabel="V_l_ratio",
    title="Duration vs Velocity Ratio")

scatter!(ax2, df_vl.duration_s, df_vl.V_l_ratio,
    color=:green, alpha=0.6, markersize=6)

# Add trend line for V_l_ratio (remove any remaining NaNs)
valid_idx2 = .!isnan.(df_vl.duration_s) .& .!isnan.(df_vl.V_l_ratio)
if sum(valid_idx2) > 0
    x_valid2 = df_vl.duration_s[valid_idx2]
    y_valid2 = df_vl.V_l_ratio[valid_idx2]
    x_range2 = range(minimum(x_valid2), maximum(x_valid2), length=100)
    X2 = hcat(ones(length(x_valid2)), x_valid2)
    β2 = X2 \ y_valid2
    trend_y2 = β2[1] .+ β2[2] .* x_range2
    lines!(ax2, x_range2, trend_y2, color=:red, linewidth=2, linestyle=:dash)
end
ylims!(ax2, 0, 1)
# text!(ax2, 0.05, 0.95, "r = $(round(corr_duration_vl, digits=4))", space=:relative, fontsize=12, color=:black)

f_corr
```

```{julia}
using CategoricalArrays
using NaNStatistics
# Binned analysis
duration_bins = [0, 2, 5, 10, 20, 50, maximum(df_corr.duration_s)]
df_binned = @transform(df_corr,
    :duration_bin = cut(:duration_s, duration_bins, labels=["0-2s", "2-5s", "5-10s", "10-20s", "20-50s", ">50s"]))

binned_stats = @chain df_binned begin
    dropmissing([:Q_sonnerup, :V_l_ratio])
    groupby(:duration_bin)
    @combine(
        :count = length(:duration_s),
        :mean_duration = nanmean(:duration_s),
        :mean_Q_sonnerup = nanmean(abs.(:Q_sonnerup)),
        :std_Q_sonnerup = nanstd(abs.(:Q_sonnerup)),
        :mean_V_l_ratio = nanmean(:V_l_ratio),
        :std_V_l_ratio = nanstd(:V_l_ratio)
    )
end

println("Mean Alfvénicity by Duration Bins:")
select(binned_stats, :duration_bin, :count, :mean_Q_sonnerup, :mean_V_l_ratio)
```

```{julia}
# Add binned averages to the scatter plots
for (i, row) in enumerate(eachrow(binned_stats))
    if i < nrow(binned_stats)
        # Get bin boundaries
        bin_start = duration_bins[i]
        bin_end = duration_bins[i+1]
        bin_center = (bin_start + bin_end) / 2

        # Add mean points with error bars to Q_sonnerup plot
        scatter!(ax1, [bin_center], [row.mean_Q_sonnerup],
            color=:red, markersize=12, marker=:diamond)
        errorbars!(ax1, [bin_center], [row.mean_Q_sonnerup], [row.std_Q_sonnerup],
            color=:red, whiskerwidth=8, linewidth=2)

        # Add mean points with error bars to V_l_ratio plot  
        scatter!(ax2, [bin_center], [row.mean_V_l_ratio],
            color=:red, markersize=12, marker=:diamond)
        errorbars!(ax2, [bin_center], [row.mean_V_l_ratio], [row.std_V_l_ratio],
            color=:red, whiskerwidth=8, linewidth=2)
    else
        # Handle the last bin (>50s) - use a representative position
        bin_center = 60  # Approximate position for >50s bin

        scatter!(ax1, [bin_center], [row.mean_Q_sonnerup],
            color=:red, markersize=12, marker=:diamond)
        errorbars!(ax1, [bin_center], [row.mean_Q_sonnerup], [row.std_Q_sonnerup],
            color=:red, whiskerwidth=8, linewidth=2)

        scatter!(ax2, [bin_center], [row.mean_V_l_ratio],
            color=:red, markersize=12, marker=:diamond)
        errorbars!(ax2, [bin_center], [row.mean_V_l_ratio], [row.std_V_l_ratio],
            color=:red, whiskerwidth=8, linewidth=2)
    end
end

# Add legend explaining the red diamonds
Legend(f_corr[2, :], [MarkerElement(color=:red, marker=:diamond, markersize=12)],
    ["Binned Averages ± Std"], orientation=:horizontal, tellwidth=false, tellheight=true)

f_corr
```

### 2025-09-03 notebooks/10_results.qmd
update
feat: add cross_helicity and residual energy

```{julia}
using DrWatson
using PSPAnisotropy.Dataset: load_all
using Discontinuity: var_mapping
import Beforerr: easy_save
using GLMakie, AlgebraOfGraphics
m = var_mapping()
df = PSPAnisotropy.workload()
```

@@

```{julia}
begin
    df = reduce(
        vcat,
        [psp_df, thm_df, wind_df, solo_df],
        cols=:intersect
    )
    levels!(df.dataset, ds_order)

@@

```{julia}
# plot the density distribution of the thickness and current density
begin
    fname = "properties_distribution"

    maps = [l_log_map j_log_map
        l_norm_log_map j_norm_log_map]
    figure_kwargs = (size=(800, 600),)

    plot_dist(data_layer; maps, axis=(), visual=mapping(), figure_kwargs=figure_kwargs)
    easy_save(fname)
end
```

>>>>

```{julia}
using DrWatson
import Beforerr: easy_save
using GLMakie, AlgebraOfGraphics
df = PSPAnisotropy.workload()
```

@@

```{julia}
begin
    df = reduce(
        vcat,
        [psp_df, thm_df, wind_df, solo_df],
        cols=:intersect
    )

@@

### 2025-09-03 notebooks/11_spectra.qmd
feat: add cross_helicity and residual energy

@@

```{julia}
using PlasmaFormulary

>>>>

# Cross helicity and residual energy

```{julia}
using Dates
using PSPAnisotropy
using PSPAnisotropy: Wind
using SPEDAS
using DimensionalData
using Unitful
using PlasmaFormulary
using TimeseriesUtilities
Unitful.preferunits(u"nA", u"km")
```

## Global (whole interval) average

```{julia}

tmin = DateTime("2007-07-06")
tmax = tmin + Hour(1)
B = DimArray(Wind.B_GSE(tmin, tmax); add_unit=true)
V = DimArray(Wind.V_GSE_3DP(tmin, tmax); add_unit=true) |> dropna
n = DimArray(Wind.n_p_3DP(tmin, tmax); add_unit=true) |> dropna
# B, V, n = SPEDAS.tsync(B, V, n)
```

```{julia}
using LinearAlgebra
using Statistics
using SPEDAS.Tullio
using TimeseriesUtilities.VectorizedStatistics

function fast_cross_helicity(B, V, n)
    N = size(B, 1)
    @tullio V_B[i, j] := Alfven_velocity(B[i, j], n[i], 1)
    @tullio B̄[j] := V_B[i, j]
    @tullio V̄[j] := V[i, j]
    B̄ .= B̄ ./ N
    V̄ .= V̄ ./ N
    @tullio num := (V_B[i, j] - B̄[j]) * (V[i, j] - V̄[j])
    @tullio den := (V_B[i, j] - B̄[j]) * (V_B[i, j] - B̄[j]) + (V[i, j] - V̄[j]) * (V[i, j] - V̄[j])
    return 2 * num / den
end

@b fast_cross_helicity(B, V, n), cross_helicity(B, V, n)
```

## Cross helicity and residual energy spectra

@@

```{julia}
